---
title: "Data 607 Assignment  Web APIs"
author: "Yohannes Deboch"
date: "28/03/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The New York Times web site provides a rich set of APIs, as described here: http://developer.nytimes.com/docs
You'll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and
transform it to an R dataframe.


# Load the libraries

```{r}
library(DT)
library(kableExtra)
library(dplyr)
library(RCurl)
library(rjson)
library(RJSONIO)
library(jsonlite)

library(httr)
library(stringr)
library(ggplot2)

library(jsonlite)
library(httr)
```

Set API Key

```{r}
apikey <- "N0kJIGXMAFAshBqvy9DQSEHG1IVArmH6"
```

Get the data

```{r}
# make the url

url <- paste0("https://api.nytimes.com/svc/books/v3//lists/current/hardcover-fiction.json?api-key=",apikey)

fictionbooks <- GET(url)
```

#Check response status

```{r}
fictionbooks$status_code
```

Convert to data frame 


```{r}
fictiondf <- fromJSON(url, flatten = TRUE)
fictiondf <- fictiondf$results
fictiondf <- fictiondf$books

#datatable(fictiondf)

jsonR <- tbl_df(as.data.frame(fictiondf))
jsonR %>% kable() %>% 
  kable_styling(bootstrap_options = "striped", font_size = 10) %>% 
  scroll_box(height = "500px", width = "100%")


```

## Conclusion 

The New York Times Book Review API is a weekly paper-magazine supplement to The New York Times in which current non-fiction and fiction books are reviewed. It is one of the most influential and widely read book review publications in the industry that lets users to get book reviews displayed by ISBN,name of author and title
